Percussive Sound Generation with Virtual Listeners and Modular Synthesizers

### 2020-01-31 paper.tex
Updates from Overleaf

\subsection{Data And Project Replication}
\label{data}
\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
\colorbox{green!=30}{need to finalize database}\\
\colorbox{blue!=30}{Should this section be at the start of the paper?The End? Appendix?}\\
talk about  categories, sources, data processing. 
Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
Give link for people to download it, show where to find the scripts for database expansion.
\section{Implementation}
\label{impl}
\subsection{Virtual Synthesizer}
We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}. This library uses a C back-end and focuses on fast offline generation of audio signals. In our implementation, a synthesizer can have any number of submodules. The parameters that deterministically dictate the output signal of the submodule as well as the range of values each paramter can take are shown in table 1 \ref{table:1} We call this number the \textit{stack size}. For the range of parameters each submodule can take. We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).  Each submodule can make an audio signal with the length of 0.1-1 second. If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
\begin{table}[h!]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{ |c|c|c| } 
\hline
Parameters & Value Range & notes and constraints\\
\hline \hline
Attack & 0-3 & A-D-S-R values relative\\
Decay & 0-3 & relative to A-S-R\\
Sustain & 0-3 & relative to A-D-R\\
Release & 0-3 & relative to A-D-S\\
OSC type & sine,square,saw & tone type\\
IsNoise & boolean & whether to generate noise\\
Sample Length & 0-1 second & - \\
StartTime & 0-1 second & Length+Start<1\\
Amplitude & 0.1-1 & 1 = max amplitude\\
Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
HP filter Cuttoff & 0-20000 & -\\
LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
Filter Order & 4,8,16 & butterworth filter order \\
\hline
\end{tabular}}
\caption{Synthesizer Submodule Parameters. Despite the simplicity of the paramters and our efforts at constraining the ranges, the number of paramters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
\label{table:1}
\end{table}
\begin{figure}[h!]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.3\linewidth]{example-image-a}
\includegraphics[width=0.3\linewidth]{example-image-b}
\includegraphics[width=0.3\linewidth]{example-image-c}
\caption{64 stack}\label{fig:64stack}
\setcounter{subfigure}{0}%
\end{subfigure}

\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.3\linewidth]{example-image-a}
\includegraphics[width=0.3\linewidth]{example-image-b}
\includegraphics[width=0.3\linewidth]{example-image-c}
\caption{8 stacks}\label{fig:8stacl}
\setcounter{subfigure}{1}%
\end{subfigure}

\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.3\linewidth]{images/specplot.png}
\includegraphics[width=0.3\linewidth]{images/specplot.png}
\includegraphics[width=0.3\linewidth]{images/specplot.png}
\caption{1 stack}\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{Examples of mel-spectrum representations of randomly generated samples. Bigger stacks give us more complex signals, but we find that even stacks of size 1 can be powerful with the right parameters. \colorbox{green!=40}{update this with actual spectrums}}
\label{fig:stackspectrums}
\end{figure}

@@

\item Frequency Transformation: A static, normalized snap-shot of the the frequencies present within the audio. The calculation of this feature vector is similar to the envelope's, but the summation is along the frequency axis. Another important distinction is that since capturing an adequate frequency resolution is important for this transformation, we utilized shorter hop-sizes and wider windows. A Mel Scale transformation was also applied in hopes that the captured features better represent human perception of frequencies. 

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{images/cnn_ear.png}
\caption{confusion matrix of the model working well on a test set. \colorbox{green!=30}{will be updated with new ear.}}
\label{fig:ok ear}
\end{figure}
\todo[inline,color=green!30]{ will add f-measure calculations and other confidence inducing graphs (for example I have a grid of spectrums with the ear's guess vs the actual label under each spectrum, I can colorize the grid depending on whether the guess was correct or not). Code in the notebooks. After updating ear, I will make them look presentable and add them.}
%
% How Can The Synth and Ear Interact?
%
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{images/random_ranks.png}
\caption{\colorbox{green!=40}{labels bigger + show other stack sizes} Showing proportions of categorical ranks for around 50,000 randomly generated sounds. Only showing ranks 1-5. About 90\% received the rank of 1 (blue portion of the bar) for the "synth" category, meaning that the ear correctly gave the highest probability to the sound being from a synth combination. We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
\todo[inline, color=blue!30]{When looking for the best sounds of each category, could use ranks 2 and 3 etc. as well, however:
\unexpanded{\unexpanded{
\begin{itemize}
    \item We must figure out how to penalize their parameters
    \item The task requires even more confidence in ear,
\end{itemize} 
}}}

\label{fig:rank portions}
\end{figure}
\subsection{How Can The Synth and Ear Interact?}

\begin{figure*}[htbp]
	\centering
		\includegraphics[width=0.7\textwidth]{images/SSS_gen.png}
	\caption{\colorbox{green!=40}{ This graph is bad in many ways.} but would it be worthwhile to have a \textbf{good} flowchart of 
	the generation pipeline in the paper? }
	\label{fig:BlockDiagram2}
\end{figure*}
\label{fig:generation}

With our Synth and Ear in place, we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample. If the ear returns a vector of categorical probabilities, we can assign categorical ranks to the audio sample. For example, the category with the highest probability will have the rank of 1, second highest would rank 2nd, and the lowest probability will have the rank of n (assuming n categories).\textbf{
But how can we use this to create percussion sounds?}\\\\
We utilize our tools in three different methods of generation, with their specific imlpementation discussed in section \ref{gens}.
\begin {enumerate} [label=(\roman*)]
\item Random Generation: We randomly create a drum programs until a sound belonging to our category is produced. We hypothesize that due to the speed of our experiments, it is a viable approach.
\item Multivariate Distribution Sampling: We attempt to learn the joint distribution of our parameters in order to maximize generation of a certain drum category. 
\item Genetic Search: We treat our parameters as genes and attempt to use evolutionary search algorithms to find programs that the ear deems most fit.\\
\end {enumerate} 
\todo[inline,color=blue!30]{As seen in Figure \ref{fig:rank portions}, there is a bias in random generation towards making higher ranking hats and kicks and lower ranking shakers, claps. Is this bias because of Synth structure or a problem with the ear? Will analyse further after updating ear}

\section{Novel Generations}
\label{gens}
\subsection{The Goal}
 Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category. We evaluate each method by measuring how many samples of categories \textit{kick,snare} and \textit{hat} can be produced in under a minute. Finally we show results of a survey conducted to measure the quality of these samples. 
\subsection{General Methods}
\colorbox{green!=30}{The next 3 sections will be modified heavily after the ear is updated.}
\subsubsection{Random Generation}
To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters. We have observed a bias in generations as indicated in figure \ref{gens}.\\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-a}
\includegraphics[width=0.48\linewidth]{example-image-a}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:rand-graphs}
\end{figure}
\subsubsection{Multivariate Distribution Sampling}
\colorbox{green!=40}{go over the math quick}\\
\colorbox{green!=40}{add some graphs showing learned params}\\
\colorbox{green!=40}{add graphs of learned parameters showing why it's not perfect}\\
This method is extremely fast and scalable once the parameter space is calculated. But success is limited due to well known issues with this approach. Notably that the parameter space for virtual synthesizers are often neither differentiable nor Gaussian. \cite{esling2019universal} (a couple more papers also talked about this, \colorbox{green!=40}{I have to look them up}). Currently our parameters are array indices mapping to different values for Synth components. This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors. \\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-b}
\includegraphics[width=0.48\linewidth]{example-image-b}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosen categories in under a minute}
\label{fig:multi-graphs}
\end{figure}

\subsubsection{Evolutionary Search}
We implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}. A parameter set is assumed to be an individual with each parameter being its genes. To measure an individuals fitness, we use the formula $fitness=score-rank$. As generations evolve, a Hall-of-Fame list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness. A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
A generation of $N$ individuals are initialized(randomly or using already existing ranked parameters). To create the offspring generation, each generation goes through mutations and in-place gene crossovers. The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity. If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\

\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-c}
\includegraphics[width=0.48\linewidth]{example-image-c}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:evo-graphs}
\end{figure}
\subsubsection{Survey of Generated Drums}
\label{survey}
\colorbox{green!=30}{Finalize ear,generate,make survey.} The survey will be sent out. I know a few producers who are willing to do this.
3 algorithms, 3 categories, 10 samples for each algorithm and category pair, 2 seconds to listen to each sample-> 3 minutes for listening\\
With those numbers I imagine survey will be around 5-6 minutes long.
\subsubsection{Contrasting Ear Scores With Survey Results}
\colorbox{green!=30}{pending section \ref{survey}}

\section{Summary and Conclusions}
\colorbox{green!=30}{Points I want to make:}
\begin{itemize}
    \item Our methodology was successful in generating novel examples of some percussion categories.
    \item Reiterate the importance of ear.
    \item There are potential benefits (e.g: pedagogical, software engineering, efficiency, data search, generality of solution, etc.) to separate some audio generation tasks into multiple parts, rather than throwing everything at some neural net. 
    \item With the right implementation of DSP methods to create a synth, Genetic search (viewed as too slow by previous work) is viable for finding  desired programs and parameters.
    \item Neural nets are function approximators. You don't need them if the actual function is understandable and simple...(but is our task simple enough? how do I prove it?)
    \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\
    \colorbox{green!=30}{Include some speed measurements in appendix?}
    \item ...
\end{itemize}
\section{Future Work}
\colorbox{blue!=30}{Need to think about this more}
\begin{itemize}
    \item Potential for other generative methods (e.g reinforcement learning)
    \item Making the synth's sound range more diverse while maintaining speed and efficiency
    \item Can our approach be used for VSTs?
\end{itemize}
%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.
\section{Ethical Standards}
To ensure objectivity and transparency in research and to ensure that accepted principles of ethical and professional conduct have been followed, authors should include a section “Ethical Standards” before the References, including (if relevant): information regarding sources of funding, potential conflicts of interest (financial or non-financial), informed consent if the research involved human participants, statement on welfare of animals if the research involved animals.

\appendix
%Appendix A
\section{section A}
In case I need an appendix
\subsection{Example Subsection}
\section{Section B}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments

%%% Place this com
\bibliographystyle{abbrv}
    \bibliography{nime-references} 
\end{document}

>>>>

\subsection{Data And Project Replication}
\label{data}
\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
\colorbox{green!=30}{need to finalize database}\\
\colorbox{blue!=30}{Should this section be at the start of the paper?The End? Appendix?}\\
talk about  categories, sources, data processing. 
Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
Give link for people to download it, show where to find the scripts for database expansion.
\section{Implementation}
\label{impl}
\subsection{Virtual Synthesizer}
We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}. This library uses a C back-end and focuses on fast offline generation of audio signals. In our implementation, a synthesizer can have any number of submodules. The parameters that deterministically dictate the output signal of the submodule as well as the range of values each paramter can take are shown in table 1 \ref{table:1} We call this number the \textit{stack size}. For the range of parameters each submodule can take. We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).  Each submodule can make an audio signal with the length of 0.1-1 second. If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
\begin{table}[h!]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{ |c|c|c| } 
\hline
Parameters & Value Range & notes and constraints\\
\hline \hline
Attack & 0-3 & A-D-S-R values relative\\
Decay & 0-3 & relative to A-S-R\\
Sustain & 0-3 & relative to A-D-R\\
Release & 0-3 & relative to A-D-S\\
OSC type & sine,square,saw & tone type\\
IsNoise & boolean & whether to generate noise\\
Sample Length & 0-1 second & - \\
StartTime & 0-1 second & Length+Start<1\\
Amplitude & 0.1-1 & 1 = max amplitude\\
Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
HP filter Cuttoff & 0-20000 & -\\
LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
Filter Order & 4,8,16 & butterworth filter order \\
\hline
\end{tabular}}
\caption{Synthesizer Submodule Parameters. Despite the simplicity of the paramters and our efforts at constraining the ranges, the number of paramters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
\label{table:1}
\end{table}
\begin{figure*}[h]
\centering

\begin{subfigure}[b]{\linewidth}
\includegraphics[width=1\linewidth]{images/ff1.pdf}
\caption{Organic hat sample}\label{fig:64stack}
\setcounter{subfigure}{1}%
\includegraphics[width=1\linewidth]{images/ff2.pdf}
\caption{Randomly generated audio with percussive qualities, resembling a tight snare}\label{fig:64stack}
\setcounter{subfigure}{2}%
\includegraphics[width=1\linewidth]{images/ff3.pdf}
\caption{A randomly generated noise with a percussive envelop but non-percussive frequency features (modulated pitch)}\label{fig:64stack}
\setcounter{subfigure}{2}%
\end{subfigure}

\caption{Graphed representation of features extracted for 3 different samples. Sample $a$ is an organic hat from our database. sample $b$ is an example of randomly generated noise with percussive qualities that we found suitably similar to a snare sound. Sample $c$ is an example of a randomly generated noise where the spectrum features are necessary for proper classification.}
\label{fig:stackspectrums}
\end{figure*}

@@

\item Frequency Transformation: A static, normalized snap-shot of the the frequencies present within the audio. The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis. Another important distinction is that since capturing an adequate frequency resolution is important for this transformation, we utilized shorter hop-sizes and wider windows. A Mel Scale transformation was also applied in hopes that the captured features better represent human perception of frequencies. 

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{images/cnn_ear.png}
\caption{confusion matrix of the model working well on a test set. \colorbox{green!=30}{will be updated with new ear.}}
\label{fig:ok ear}
\end{figure}
\todo[inline,color=green!30]{ will add f-measure calculations and other confidence inducing graphs (for example I have a grid of spectrums with the ear's guess vs the actual label under each spectrum, I can colorize the grid depending on whether the guess was correct or not). Code in the notebooks. After updating ear, I will make them look presentable and add them.}
%
% How Can The Synth and Ear Interact?
%
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{images/random_ranks.png}
\caption{\colorbox{green!=40}{labels bigger + show other stack sizes} Showing proportions of categorical ranks for around 50,000 randomly generated sounds. Only showing ranks 1-5. About 90\% received the rank of 1 (blue portion of the bar) for the "synth" category, meaning that the ear correctly gave the highest probability to the sound being from a synth combination. We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
\label{fig:rank portions}
\end{figure}

\subsection{How Can The Synth and Ear Interact?}
With our Synth and Ear in place, we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample. If the ear returns a vector of categorical probabilities, we can assign categorical ranks to the audio sample. For example, the category with the highest probability will have the rank of 1, second highest would rank 2nd, and the lowest probability will have the rank of n (assuming n categories).\textbf{
But how can we use this to create percussion sounds?}\\\\
We utilize our tools in three different methods of generation, with their specific imlpementation discussed in section \ref{gens}.
\begin {enumerate} [label=(\roman*)]
\item Random Generation: We randomly create a drum programs until a sound belonging to our category is produced. We hypothesize that due to the speed of our experiments, it is a viable approach.
\item Multivariate Distribution Sampling: We attempt to learn the joint distribution of our parameters in order to maximize generation of a certain drum category. 
\item Genetic Search: We treat our parameters as genes and attempt to use evolutionary search algorithms to find programs that the ear deems most fit.\\
\end {enumerate} 
\todo[inline,color=blue!30]{As seen in Figure \ref{fig:rank portions}, there is a bias in random generation towards making higher ranking hats and kicks and lower ranking shakers, claps. Is this bias because of Synth structure or a problem with the ear? Will analyse further after updating ear}

\section{Novel Generations}
\label{gens}
\subsection{The Goal}
 Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category. We evaluate each method by measuring how many samples of categories \textit{kick,snare} and \textit{hat} can be produced in under a minute. Finally we show results of a survey conducted to measure the quality of these samples. 
\subsection{General Methods}
\colorbox{green!=30}{The next 3 sections will be modified heavily after the ear is updated.}
\subsubsection{Random Generation}
To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters. We have observed a bias in generations as indicated in figure \ref{gens}.\\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-a}
\includegraphics[width=0.48\linewidth]{example-image-a}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:rand-graphs}
\end{figure}
% \subsubsection{Multivariate Distribution Sampling}
% This method is extremely fast and scalable once the parameter space is calculated. But success is limited due to well known issues with this approach. Notably that the parameter space for virtual synthesizers are often neither differentiable nor Gaussian. \cite{esling2019universal} (a couple more papers also talked about this, \colorbox{green!=40}{I have to look them up}). Currently our parameters are array indices mapping to different values for Synth components. This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors. \\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-b}
\includegraphics[width=0.48\linewidth]{example-image-b}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosen categories in under a minute}
\label{fig:multi-graphs}
\end{figure}

\subsubsection{Evolutionary Search}
We implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}. A parameter set is assumed to be an individual with each parameter being its genes. To measure an individuals fitness, we use the formula $fitness=score-rank$. As generations evolve, a Hall-of-Fame list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness. A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
A generation of $N$ individuals are initialized randomly. To create the offspring generation, each generation goes through mutations and in-place gene crossovers. The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity. If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\
\subsubsection{Survey of Generated Drums}
\label{survey}
To measure the quality of the samples produced by our pipeline, we randomly generated around 50-60 samples in the following categories: "snare","kick","hat","clap" and "other" (combination of rims,shakers, and unusal percussive sounds"). These samples were determined to be percussive and then categorized by 4 different models (FC,CNNLSTM,E+F and AVG). We ensured a balanced division between samples of stack sizes 1,2 and 4 (each stack is responsible for a third samples under each category). Both writers then categorized these samples without knowledge of other categorizations (human or computation models). It's important to note that:
\begin{itemize}
    \item Humans had an additional category of "bad" for samples that they deemed not appropriate. 
    \item Human's had the same categorization in 47\% of cases
    \item The agreement between the authors and AVG was 44\% and 47\%, not significantly lower than agreement with each other. 
    \item Of 257 samples, both authors agreed with FC, CNNLSTM, AVG and E+F respectively in 78,76,76 and 46 of cases.
\end{itemize}
We assess the reliability of agreement between humans and categorization models via the Fleiss' kappa coefficient. The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicating perfect agreement. Our kappa measurements \ref{kappa_table} lie in within the 3.5-4.5 range, indicating mild to moderate agreement between humans and machines. We again measure this coefficient after dropping samples that were categorized as "bad" by the authors, as samples that humans deem to be "bad" indicate a failure in phase 1 and arguably should not have been categorized by the models at all. Dropping of samples that both authors deemed "bad" causes 8\% reduction of our data (21 samples) and a small increase in kappa score. Dropping samples either reviewer deemed bad resulted in a 30\% reduction of samples and relatively large increase in kappa scores. \\
\begin{center}
\begin{table}

 \begin{tabular}{||c c c c c c||} 
 \hline
 DropBad? & Sample Size & HvH & H+FC & H+CNN & H+ALL \\ [0.5ex] 
 \hline
 No & 257 &0.37 & 0.35 & 0.35 & 0.36 \\ 
 \hline
 Yes(if both)& 236 & 0.31 & 0.37 & 0.37 & 0.38 \\
 \hline
 Yes(if either)& 180 & 0.47 & 0.50 & 0.48 & 0.46 \\
 \hline

\end{tabular}
\caption{\label{kappa_table}Table of Fleiss' kappa coefficient to measure the degree of agreement between humans (HvH), humans and FC model (H+FC), humans and CNNLSTM model and humans and all models (H+ALL)}
\end{table}

\end{center}

\section{Summary and Conclusions}

\begin{itemize}
    \item Our methodology was successful in generating novel examples of some percussion categories.
    \item Reiterate the importance of ear.
    \item There are potential benefits (e.g: pedagogical, software engineering, efficiency, data search, generality of solution, etc.) to separate some audio generation tasks into multiple parts, rather than throwing everything at some neural net. 
    \item With the right implementation of DSP methods to create a synth, Genetic search (viewed as too slow by previous work) is viable for finding  desired programs and parameters.
    \item Neural nets are function approximators. You don't need them if the actual function is understandable and simple...(but is our task simple enough? how do I prove it?)
    \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\
    \colorbox{green!=30}{Include some speed measurements in appendix?}
    \item ...
\end{itemize}
\section{Future Work}
\colorbox{blue!=30}{Need to think about this more}
\begin{itemize}
    \item Potential for other generative methods (e.g reinforcement learning)
    \item Making the synth's sound range more diverse while maintaining speed and efficiency
    \item Can our approach be used for VSTs?
\end{itemize}

\section{Ethical Standards}
We affirm that our work follows the principles of ethical and professional conduct.
\bibliographystyle{abbrv}
    \bibliography{nime-references} 
\end{document}
